Calculating Entropies With Nested Sampling

### 2017-02-22 paper/ms.tex
Some NS talk

Nested Sampling \citep[NS][]{skilling2006nested}

>>>>

Nested Sampling \citep[NS][]{skilling2006nested} is an algorithm whose aim is
to calculate the marginal likelihood
\begin{align}
Z &= \int \pi(\x) L(\x) \, d\x
\end{align}
where $\x$ is the unknown parameter(s), $\pi$ is the prior distribution,
and $L$ is the likelihood function. It does this evolving a population of
$N$ particles in the parameter space.

Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}

The $N$ particles are initially initialised from the prior $\pi(\x)$, and the
particle with the lowest likelihood.
